IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex
capitalize titles.

\subsection{IFC language features}
\label{sec:extensions:labeled}

@@

\subsection{Type safety}
\label{sec:extensions:types}

@@

\subsection{Scheduling policies}
Our specification language is parametrized by a scheduling policy
|alpha|, which maps a task list to a potentially different task list.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
For simplicity we considered two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies that only
rely on the current task list.
%
For example, this allows us to implement the scheduler of~\cite{Kashyap:2011}
that always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DCLabels~\cite{myers:dlm,dclabels}, this scheduling policy is
  considerably more complex. See~\cite{Kashyap:2011}.
}
%
More generally, we believe that deterministic schedulers that always
make ``low-progress,'' i.e., if a task whose label is not above the
current task's label will will eventually run, and do not decide which
low tasks to schedule according to data more sensitive than the tasks'
label, i.e., the scheduler does not schedule one public thread over
another according to sensitive data, to be safe.
%

@@

\subsection{External effects}
\label{sec:extensions:external}
Our embedding assumes that the target language not have any
primitives that can external-world effects.
%
Indeed, as discussed in Section~\ref{sec:real}, part of the challenge
when considering real languages is precisely imposing this restriction
on the concrete implementation.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in our modified IFC browser must load resources or
perform XHR to be useful.

>>>>

\subsection{IFC Language Features}
\label{sec:extensions:labeled}

@@

\subsection{Type Safety}
\label{sec:extensions:types}

@@

\subsection{Scheduling Policies}
Our specification language is parametrized by a scheduling policy
|alpha|, which maps a task list to a potentially different task list.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
For simplicity we considered two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies that only
rely on the current task list.
%
For example, this allows us to implement the scheduler of~\cite{Kashyap:2011}
that always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DCLabels~\cite{myers:dlm,dclabels}, this scheduling policy is
  considerably more complex. See~\cite{Kashyap:2011}.
}
%
More generally, we believe that deterministic schedulers that always
make ``low-progress,'' i.e., if a task whose label is not above the
current task's label will will eventually run, and do not decide which
low tasks to schedule according to data more sensitive than the tasks'
label, i.e., the scheduler does not schedule one public thread over
another according to sensitive data, to be safe.
%

@@

\subsection{External Effects}
\label{sec:extensions:external}
Our embedding assumes that the target language not have any
primitives that can external-world effects.
%
Indeed, as discussed in Section~\ref{sec:real}, part of the challenge
when considering real languages is precisely imposing this restriction
on the concrete implementation.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in our modified IFC browser must load resources or
perform XHR to be useful.

### 2014-03-02 paper/retrofit.tex
capitalize titles.

\section{Retrofitting languages with IFC}
\label{sec:retrofit}

@@

\subsection{Target language: Mini-ES}

@@

\subsection{IFC language}

@@

\subsection{The embedding}
Figure~\ref{fig:embedding}
provides all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:

>>>>

\section{Retrofitting Languages with IFC}
\label{sec:retrofit}

@@

\subsection{Target Language: Mini-ES}

@@

\subsection{IFC Language}

@@

\subsection{The Embedding}
Figure~\ref{fig:embedding}
provides all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:
